The Overlapping Control Volume Finite Element Method for Multiphase Porous Media Flow Modelling \\ Part I: Numerical Formulation

### 2015-01-21 Papers/Prototype_1_Method/article_figure1.tex
Paper 1 is updated taking into account comments from Pain, Percival and Jackson. Different from the previous version of the paper (under SVN), results of the Buckley-Leverett problems in 1-3D were introduced (based on existing plots and comments of Prototype Paper 2

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{-0.5cm}\includegraphics[width=.6\textwidth]{diagrams/p0dgp1-cont-sat} 
\hspace{-.9cm}\includegraphics[width=.6\textwidth]{diagrams/p1dgp2-cont-sat} }
\hbox{\hspace{4cm}(a) \hspace{6.5cm}(b)}
\vspace{0.cm}
\hbox{\hspace{2.5cm}\includegraphics[width=.8\textwidth]{diagrams/p2dgp1-dg-sat} }
\vspace{-0.3cm}
\hbox{\hspace{6cm}(c) }
}
\caption{2D representation of the element-pairs (a) P0DGP1, (b) P1DGP2  and (c) P2DGP1DG. Shaded areas denote a control volumes (in which saturation is stored), black points represent the pressure nodes and the white points the velocity.}
  \label{fem_cv_represent_a}
\end{figure}

@@

\begin{figure}[htp]
\begin{center}
\hbox{\hspace{-2.cm}
\includegraphics[width=1.3\textwidth,height=1.3\textwidth]{diagrams/overlapping_cartoon}}
\vspace{-1.4cm}
\caption{Diagram showing the exact representation of Darcy's law in 1D. From top to bottom, the plots show i) a P2 continuous pressure field, $p$, across three elements, ii) the P1DG gradient of that  pressure field, iii) a P0DG absolute permeability field, ${\bf K}$, iv) a CV mobility field, $\lambda_{k}=\frac{\mathcal{K}_{rk}\left(S_{k}\right)}{\mu_{k}}$, and finally v) the resultant CV0DG velocity field arising from Darcy's law. Here dashed lines denote the boundaries of the P2 finite element mesh, dotted lines denote boundaries between the control volumes dual to the P2 mesh and solid dots indicate the natural locations of degrees of freedom in a non-overlapping formulation. }
\label{fig:darcys_law}
\end{center}
\end{figure}

>>>>

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{-0.5cm}\includegraphics[width=.6\textwidth]{diagrams/p0dgp1-cont-sat} 
\hspace{-.9cm}\includegraphics[width=.6\textwidth]{diagrams/p1dgp2-cont-sat} }
\hbox{\hspace{4cm}(a) \hspace{6.5cm}(b)}
\vspace{0.cm}
\hbox{\hspace{2.5cm}\includegraphics[width=.8\textwidth]{diagrams/p2dgp1-dg-sat} }
\vspace{-0.3cm}
\hbox{\hspace{6cm}(c) }
}
\caption{2D representation of the element-pairs (a) \PN[0]{1}, (b) \PN[1]{2} and (c) \PNDG[2]{1}. Shaded areas denote a control volumes (in which saturation is stored), black points represent the pressure nodes and the white points the velocity.}
  \label{fem_cv_represent_a}
\end{figure}

@@

\begin{figure}[htp]
\begin{center}
\hbox{\hspace{-2.cm}
\includegraphics[width=1.3\textwidth,height=1.3\textwidth]{diagrams/overlapping_cartoon}}
\vspace{-1.4cm}
\caption{Diagram showing the exact representation of Darcy's law in 1D. From top to bottom, the plots show i) a P$_{2}$ continuous pressure field, $p$, across three elements, ii) the P$_{1}$DG gradient of that  pressure field, iii) a P$_{0}$DG absolute permeability field, ${\bf K}$, iv) a CV mobility field, $\lambda_{k}=\frac{\mathcal{K}_{rk}\left(S_{k}\right)}{\mu_{k}}$, and finally v) the resultant CV$_{0}$DG velocity field arising from Darcy's law. Here dashed lines denote the boundaries of the P$_{2}$ finite element mesh, dotted lines denote boundaries between the control volumes dual to the P$_{2}$ mesh and solid dots indicate the natural locations of degrees of freedom in a non-overlapping formulation. }
\label{fig:darcys_law}
\end{center}
\end{figure}

### 2015-01-21 Papers/Prototype_1_Method/article_figure2.tex
Paper 1 is updated taking into account comments from Pain, Percival and Jackson. Different from the previous version of the paper (under SVN), results of the Buckley-Leverett problems in 1-3D were introduced (based on existing plots and comments of Prototype Paper 2

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from the discontinuous and continuous formulations with different mesh resolutions. Solutions with (top) and without (bottom) upwinding scheme. Notice that oscillations are suppressed with the upwinding scheme.\label{bl-dg-cent-4-10-20}}
\end{figure}

>>>>

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from the discontinuous and continuous formulations with different mesh resolutions. Solutions without (top) and with (bottom) upwinding scheme. Notice that oscillations are suppressed with the upwinding scheme.\label{bl-dg-cent-4-10-20}}
\end{figure}
